---
title: "FoodRegfMRI: Behavioral Analyses"
output: html_notebook
---
# SETUP
## Import libraries & Load Data

```{r}
# Import Libraries
library(tidyverse)
library(lme4)
library(car)
library(ggplot2)
library(lmerTest)
library(broom)
library(data.table)
library(pander)
#devtools::install_github("neuropsychology/psycho.R")

# Load helper functions
source("r_scripts/helper_functions.R")

# Load Data
load("data/FoodRegfMRI_dt.RData")
dt = full_dt
```

## Manipulate Data Table
```{r}
# add some columns and center predictors, remove NA rows
dt = process_data_table(dt)

# Make condition dts
dt_nat = dt[dt$cond == "Respond Naturally",]
dt_health = dt[dt$cond == "Focus on Healthiness",]
dt_dd = dt[dt$cond == "Decrease Desire",]

# means by subject and by condition
  # and calculate health/taste change w/baseline
dt_subj = by_subject(dt)

# Load Hause helper functions (for some reason it breaks the by_subject() function if run first)
source("https://raw.githubusercontent.com/hauselin/Rcode/master/summaryh.R")
source("https://raw.githubusercontent.com/hauselin/Rcode/master/se.R")
```

## Response Variability (by Condition)
```{r}
# SUBJECT/RESPONSE
sub_response_variability <- dt %>%
  group_by(cond, subject, block) %>%
  dplyr::summarise(sd = sd(resp, na.rm = T), resp=mean(resp, na.rm=T), n = n())

pander(sub_response_variability)

# how many of each response in each block
resp_count = dt %>%
  group_by(subject, cond, block, resp) %>%
  dplyr::summarise(pref=mean(resp, na.rm=T), count = n())

# how many trials in each block (accounts for missed trials)
block_count = resp_count %>%
  group_by(subject, cond, block) %>%
  dplyr::summarise(count=sum(count)) 

# take the most common response (randomly selecting one resp in case of ties)
resp_count2 = resp_count %>%
  group_by(subject, cond, block) %>%
  filter(count == max(count)) %>%
  slice(1)

# add total count and diff columns
resp_count2$trial_count = block_count$count
resp_count2 = resp_count2 %>%
  mutate(diff = trial_count - count)

# curious if this is mostly the Decrease condition?
cond_var = filter(resp_count2, diff<2)
cond_var %>%
  group_by(cond) %>%
  summarise(count <=1)           

# ALL SUBJECTS
# NO variation
var_0 = filter(resp_count2, diff==0)
length(var_0$block)
# SINGLE variation
var_1_0 = filter(resp_count2, diff<=1)
length(var_1_0$block)

# GOOD SUBJECTS
good_subjects = c(101:104, 106:112, 114, 116, 118:121, 123:126, 129:137, 139:140, 142:148, 150, 152:158, 162:164)
# NO variation
var_0_good = var_0[var_0$subject %in% good_subjects,]
length(var_0_good$block)
# SINGLE variation
var_1_0_good = var_1_0[var_1_0$subject %in% good_subjects,]
length(var_1_0_good$block)
length(unique(var_1_0_good$subject))

subs = var_1_0_good %>%
  group_by(subject) %>%
  summarise(n_blocks = n())

filter(subs, n_blocks>5)
plot(subs)

# CORR HEALTH TASTE
health_taste_corr = dt %>%
  group_by(subject) %>%
  dplyr::summarise(corr = cor(health, taste))

ggplot(health_taste_corr) +
  geom_point(aes(subject-100, corr))

# bimodal?
hist(health_taste_corr$corr, breaks = 12)

# 18 subjects have a correlation over 0.3
filter(health_taste_corr, corr>0.3)
# 29 negative corr
filter(health_taste_corr, corr<0)

# CORR Post-Pre and Health
health_postPre_corr = dt %>%
  group_by(subject) %>%
  dplyr::summarise(corr = cor(health, post_pre))

ggplot(health_postPre_corr) +
  geom_point(aes(subject-100, corr))

# normal and centered around zero
mean(health_postPre_corr$corr)
hist(health_postPre_corr$corr)

# GROUP/RESPONSE
group_response_variability = dt %>%
  group_by(cond) %>%
  dplyr::summarise(sd = sd(resp, na.rm=T)) %>%
  pander()

# SUBJECT/CHOICE
sub_choice_variability <- dt %>%
  group_by(cond, subject) %>%
  dplyr::summarise(sd = sd(choice, na.rm = TRUE), resp=mean(choice, na.rm=T), n = n())

pander(sub_choice_variability)

ggplot(sub_choice_variability) +
  geom_point(aes(subject-100, sd, color=cond))

# SUBJECT/PRE-LIKING
pre_liking_variability <- dt %>%
  group_by(subject) %>%
  dplyr::summarise(sd = sd(pre_liking, na.rm = TRUE), pre_liking = mean(pre_liking, na.rm = TRUE), n = n()) %>%
  pander()

# SUBJECT RESP
resp_variability <- dt %>%
  group_by(subject) %>%
  dplyr::summarise(sd = sd(resp, na.rm = TRUE), resp = mean(pre_liking, na.rm = TRUE), n = n()) %>%
  pander()

# COR pre-liking and resp variability
cor(resp_variability$sd, pre_liking_variability$sd)

```

```{r}
df_hddm = dt %>%
  rename(subj_idx = subject, response=choice)

df_hddm$cond = dplyr::recode(df_hddm$cond, "Respond Naturally" = "Natural", "Decrease Desire" = "Decrease","Focus on Healthiness" = 'Health')

write.csv(df_hddm, file = "hddm/data/foodreg_fmri.csv")
```

## Add Slopes for Taste/Health
```{r}
# Use resp instead of choice to calculate slopes
# Natural
model_nc <- glmer(choice ~ taste_c + health_c + (1 + taste_c + health_c|subject),
               data = dt_nat, family = binomial,
               control = glmerControl(optimizer= 'bobyqa'))

model_np <- lmer(resp ~ taste_c + health_c + (1 + taste_c + health_c|subject), 
              data = dt_nat)

model = model_np

dt_subj$intercept[dt_subj$cond=="Respond Naturally"] = coef(model)$subject[,1]
dt_subj$taste_slope[dt_subj$cond=="Respond Naturally"] = coef(model)$subject[,2]
dt_subj$health_slope[dt_subj$cond=="Respond Naturally"] = coef(model)$subject[,3]
  
# Decrease
model_dc <- glmer(choice ~ taste_c + health_c + (1 + taste_c + health_c|subject),
               data = dt_dd, family = binomial,
               control = glmerControl(optimizer= 'bobyqa'))

model_dp <- lmer(resp ~ taste_c + health_c + (1 + taste_c + health_c|subject), 
              data = dt_dd)

model = model_dp

dt_subj$intercept[dt_subj$cond=="Decrease Desire"] = coef(model)$subject[,1]
dt_subj$taste_slope[dt_subj$cond=="Decrease Desire"] = coef(model)$subject[,2]
dt_subj$health_slope[dt_subj$cond=="Decrease Desire"] = coef(model)$subject[,3]


# Health
model_hc <- glmer(choice ~ taste_c + health_c + (1 + taste_c + health_c|subject),
               data = dt_health, family = binomial,
               control = glmerControl(optimizer= 'bobyqa'))

model_hp <- lmer(resp ~ taste_c + health_c + (1 + taste_c + health_c|subject), 
              data = dt_health)

model = model_hp

dt_subj$intercept[dt_subj$cond=="Focus on Healthiness"] = coef(model)$subject[,1]
dt_subj$taste_slope[dt_subj$cond=="Focus on Healthiness"] = coef(model)$subject[,2]
dt_subj$health_slope[dt_subj$cond=="Focus on Healthiness"] = coef(model)$subject[,3]

# model with everything
# model_all <- lmer(resp ~ taste_c + health_c + cond + (1 + taste_c + health_c + cond|subject), data = dt)

# summary(model_all)

# Calculate difference of slopes with baseline (natural)
dt_subj = dt_subj %>%
  group_by(subject) %>%
  mutate( health_slope_change = health_slope - health_slope[cond=="Respond Naturally"],
          taste_slope_change = taste_slope - taste_slope[cond=="Respond Naturally"]
  )

# Label based on regulatory success (3 categories)
dt_subj = dt_subj %>%
  group_by(cond) %>%
  mutate( health_slope_change_cat = ntile(health_slope_change, 3),
          taste_slope_change_cat = ntile(taste_slope_change, 3)
  )

# Apply labels to original long dataframe
dt_merged = merge(dt, dt_subj, by=c("subject", "cond"))
```


# BASIC ANALYSIS 
## RTs
### RT by Condition
```{r}
# Reaction time by conditions
rts = se(data = dt, measurevar = "rt", groupvars = "cond")
rts

# Plot 
ggplot(rts, aes(cond, rt, color = cond)) +
  geom_point() +
  geom_errorbar(aes(ymin = rt-se, ymax = rt+se))
```
#### Stats: RT by Condition
```{r}
# Differences in RTs significant?
# It is if we use dt but not for dt_subj?
  # Which to use?
m_rt = lmer(rt ~ cond + (1 + cond|subject), data = dt)
summaryh(m_rt)
#summaryh(m_rt, showTable = T, showEffectSizesTable = T)
fit <- lmer(rt ~ cond + (1 + cond|subject), data=dt)
anova(fit)

# NOT WORKING
# contrasts = get_contrasts(fit, formula="cond", adjust="tukey")

# Anova
anova_test = dt %>%
  aov(rt ~ cond + Error(subject/cond), data=.)
anova_test %>%
  summary # Why is this p-val larger??
# anova_test %>%
#  TukeyHSD # this doesn't work with the Error specification in aov
# suggests that DD/Health not sig

# Contrasts nothing sig??
t.test(dt_subj$rt[dt_subj$cond=="Decrease Desire"], 
       dt_subj$rt[dt_subj$cond=="Focus on Healthiness"])
t.test(dt_subj$rt[dt_subj$cond=="Decrease Desire"], 
       dt_subj$rt[dt_subj$cond=="Respond Naturally"])
t.test(dt_subj$rt[dt_subj$cond=="Focus on Healthiness"],
       dt_subj$rt[dt_subj$cond=="Respond Naturally"])

# Azadeh: important to select outliers (look in natural condition)
```

### RT by Condition & Choice
```{r}
# RT by condition
rts = se(data = dt, measurevar = "rt", groupvars = c("cond", "choice"))
rts$choice = plyr::mapvalues(rts$choice, c(0,1), c('Reject', 'Accept'))
rts

# Plot 
ggplot(rts, aes(cond, rt, color = choice)) +
  geom_point() +
  geom_errorbar(aes(ymin = rt-se, ymax = rt+se))
```
Note the gap between the accept/reject RTs for DD (consistent with starting point bias)

#### Stats: RT by Condition & Choice
```{r}
# repeated measures Anova (two methods)
# RT on condition + choice
summary(aov(rt ~ cond * choice + Error(subject/(cond*choice)), data = dt, na.action = na.omit))
fit = lmer(rt ~ cond * choice + (1 + cond * choice|subject), data=dt)
anova(fit) # why so different than aov?
#analyze(fit)

# RT on condition + response (preference)
summary(aov(rt ~ cond * resp + Error(subject/(cond+resp)), data = dt, na.action = na.omit))
fit = lmerTest::lmer(rt ~ cond * resp + (1|subject), data=dt)
anova(fit) # weird. Cond is weaker with lmer but resp and interaction stronger?
# with random slopes
fit <- lmer(rt ~ cond * resp + (1 + cond*resp|subject), data=dt)
anova(fit)
#analyze(fit)
```


## Acceptance Rates
### Acceptance By Condition

```{r}
# RT by condition
accept = se(data = dt, measurevar = "choice", groupvars = "cond")
accept

# Plot 
ggplot(accept, aes(cond, choice, color = cond)) +
  geom_point() +
  geom_errorbar(aes(ymin = choice-se, ymax = choice+se))
```

#### Stats: Acceptance By Condition
```{r}
# repeated measures Anova
# Choice
summary(aov(choice~cond + Error(subject/cond), data = dt, na.action = na.omit))

fit = glmer(choice ~ cond + (1|subject),
            data = dt, family = binomial,
            control = glmerControl(optimizer= 'bobyqa'), nAGQ = 10)
anova(fit)
summaryh(fit)
```


### Preference by Condition
```{r}
# RT by condition
pref = se(data = dt, measurevar = "resp", groupvars = "cond")
pref

# Plot 
ggplot(pref, aes(cond, resp, color = cond)) +
  geom_point() +
  geom_errorbar(aes(ymin = resp-se, ymax = resp+se))
```

#### Stats: Preference by Condition
```{r}
# Response (preference)
summary(aov(resp~cond + Error(subject/cond), data = dt, na.action = na.omit))
fit = lmerTest::lmer(resp ~ cond + (1|subject), data=dt)
anova(fit)
summaryh(fit)
```


### Acceptance By Condition and Pre liking
```{r}
#dt %>%
#  group_by(cond, pre_liking) %>%
#  summarise(rate = mean(choice, na.rm=TRUE))

accept = se(data = dt, measurevar = "choice", groupvars = c("cond", "pre_liking"))
accept

# Plot 
ggplot(accept, aes(cond, choice, color = factor(pre_liking))) +
  geom_point() +
  geom_errorbar(aes(ymin = choice-se, ymax = choice+se))
```
Note that in Focus on Health the lower three ratings (compared with Natural) are *higher* and the upper three ratings are *lower*

## Correlatios of Response

### Pre-liking correlation with Preference
```{r}
dt %>%
  group_by(cond) %>%
  summarise(cor = cor(pre_liking, resp))
```

### Correlation Taste and Health with Preference by condition

```{r}
dt %>%
  group_by(cond) %>%
  summarise(cor = cor(pre_liking, taste))

dt %>%
  group_by(cond) %>%
  summarise(cor = cor(pre_liking, health))
```


# HEALTH AND TASTE
## Taste by Condition
```{r}
# Taste by Cond 
taste_weight = se(data = dt_subj, measurevar = "taste_slope", groupvars = "cond")
taste_weight
# Plot
ggplot(taste_weight, aes(cond, taste_slope, color = cond)) +
  geom_point() +
  geom_errorbar(aes(ymin = taste_slope-se, ymax = taste_slope+se))
```

## Health by Condition
```{r}
# Health by Cond 
health_weight = se(data = dt_subj, measurevar = "health_slope", groupvars = "cond")
health_weight
# Plot
ggplot(health_weight, aes(cond, health_slope, color = cond)) +
  geom_point() +
  geom_errorbar(aes(ymin = health_slope-se, ymax = health_slope+se))
```

## Intercept by Condition
```{r}
# Intercept by Cond 
int = se(data = dt_subj, measurevar = "intercept", groupvars = "cond")
int
# Plot
ggplot(int, aes(cond, intercept, color = cond)) +
  geom_point() +
  geom_errorbar(aes(ymin = intercept-se, ymax = intercept+se))
```

## Taste/Health/Int by Condition
```{r}
# Plot Simultaneously
# standardize column names and add coef column
taste_weight$coef = 'taste'
taste_weight = taste_weight%>%
  rename(beta = taste_slope)
health_weight$coef = 'health'
health_weight = health_weight%>%
  rename(beta = health_slope)
int$coef = 'intercept'
int = int%>%
  rename(beta = intercept)

# Stack
combined <- rbind(taste_weight, health_weight, int)
combined

# Plot
ggplot(combined, aes(cond, beta, color = coef)) +
  geom_point() +
  geom_errorbar(aes(ymin = beta-se, ymax = beta+se))
```

## Stats
```{r}
fit = lmerTest::lmer(resp ~ health*cond + taste*cond + (1 + health + taste|subject), data=dt)
summary(fit)
anova(fit)
psycho::analyze(fit)
```

## Weight Change by Condition
```{r}
# HEALTH
pp_health <- se(dt_subj, measurevar="health_slope_change", groupvars="cond")

# Same plot
ggplot(pp_health, aes(cond, health_slope_change, color=cond)) +
  geom_point() +
  geom_errorbar(aes(ymin = health_slope_change-se, ymax = health_slope_change+se)) 

# TASTE
pp_taste <- se(dt_subj, measurevar="taste_slope_change", groupvars="cond")

# Same plot
ggplot(pp_taste, aes(cond, taste_slope_change, color=cond)) +
  geom_point() +
  geom_errorbar(aes(ymin = taste_slope_change-se, ymax = taste_slope_change+se)) 
```


# POST PRE
## Healthy/Unhealthy
```{r}
pp_health <- se(dt, measurevar="post_pre", groupvars=c("healthy","cond"))
# Plot
ggplot(pp_health, aes(cond, post_pre, color = healthy)) +
  geom_point() +
  geom_errorbar(aes(ymin = post_pre-se, ymax = post_pre+se)) 
```

## Tasty/Untasty
```{r}
pp_taste <- se(dt, measurevar="post_pre", groupvars=c("tasty","cond"))
# Plot
ggplot(pp_taste, aes(cond, post_pre, color = tasty)) +
  geom_point() +
  geom_errorbar(aes(ymin = post_pre-se, ymax = post_pre+se)) 
```

# REGULATORY SUCCESS
## Change in Liking V Change in Health Weight (Unhealthy Foods)
Check to see if there is a correlation between the magnitude of the subject's change
in health weight and their *change in liking* of *unhealthy* foods
```{r}
# Health weight CHANGE in health condition 
hw = dt_subj$health_slope_change[dt_subj$cond=="Focus on Healthiness"]

#vs 
#PostPre Liking change in for unhealthy foods from Health Condition
pp = dt %>%
  group_by(subject) %>%
  summarise(change = mean(post_pre[cond=="Focus on Healthiness" & healthy=="unhealthy"], na.rm = TRUE))

pp$hw = hw

ggplotRegression(lm(change~hw, data = pp))
```

## Change in Liking V Change in Health Weight (Healthy Foods)
```{r}
# Health weight CHANGE in health condition 
hw = dt_subj$health_slope_change[dt_subj$cond=="Focus on Healthiness"]

#vs 
#PostPre Liking change in for HEALTHY foods from Health Condition
pp = dt %>%
  group_by(subject) %>%
  summarise(change = mean(post_pre[cond=="Focus on Healthiness" & healthy=="healthy"], na.rm = TRUE))

pp$hw = hw

ggplotRegression(lm(change~hw, data = pp))
```

## Change in Liking V Change in Health Weight (Healthy - Unhealthy Foods)
```{r}
# Health weight CHANGE in health condition 
hw = dt_subj$health_slope_change[dt_subj$cond=="Focus on Healthiness"]

#vs 
#PostPre Liking change in for HEALTHY vs UNHEALTHY foods from Health Condition
pp_healthy = dt %>%
  group_by(subject) %>%
  summarise(change = mean(post_pre[cond=="Focus on Healthiness" & healthy=="healthy"], na.rm = TRUE))

pp_unhealthy = dt %>%
  group_by(subject) %>%
  summarise(change = mean(post_pre[cond=="Focus on Healthiness" & healthy=="unhealthy"], na.rm = TRUE))

pp$change = pp_healthy$change - pp_unhealthy$change
pp$hw = hw

ggplotRegression(lm(change~hw, data = pp))
```





# Psycho Example
https://neuropsychology.github.io/psycho.R/2018/07/20/analyze_anova.html
```{r}
df <- psycho::affective  # load a dataset available in the psycho package

aov_results <- aov(Adjusting ~ Sex * Salary, data=df)  # Fit the ANOVA
summary(aov_results)  # Inspect the results
analyze(aov_results)
```